% 英文摘要
\begin{Abstract}

    This paper is not only the use document of the latex graduation thesis template of Nanchang Institute of Engineering, but also a complete example of the graduation thesis template. 
    The document includes three aspects:

    \begin{enumerate}
        \item How to use this template
        \item Principle of template design
        \item Acknowledgement
    \end{enumerate}

    The template of this graduation thesis is described in three aspects. the typesetting method of the template is in accordance with the "6-graduation Design (thesis) Writing Standard" (hereinafter referred to as "Specification"), taking into account the aesthetics after typesetting. The style of some details has been modified, which may conflict with some of the contents of the specification.

    This template refers to some of the templates designed by Song Guangchun, a senior of Grade 15 of Yaohu University, but the template of Song still has some problems, such as the complex catalog structure, the ambiguity between the template style file and the text structure, some style problems and so on. 

    This template packages all the styles into the\Code{cls}template file, and puts all the text content into the body\Code{demo.tex}document, realizing the separation of the style and the text content, making it more convenient to use. You only need to use a\Code{cls}file to generate any copy of the graduation thesis document, and you do not need to create a new directory structure to create a graduation thesis document. 

    At the same time, this document takes into account the differences between Chinese papers and English papers, and provides style support for graduation papers in both languages. It only takes one line of \LaTeX{} command to switch the document types of graduation papers between Chinese and English, and the mode of use will be described in detail below.

    At the same time, this template has made a cover including the title page, Yaohu College-level blind trial and Nangong school-level blind trial, which can be directly inserted into any location of the document with a \LaTeX{} command. The specific usage will be described in detail below.

    I am very grateful to the senior Song for providing the \LaTeX{} template, some of which I have referred to, and thanks to the \LaTeX{} communication group for helping me solve the problems of picture and subtitle typesetting.

    Of course, there are still some undiscovered problems with this template. If you have any problems in the use of this template, please contact us by email \Code{\href{mailto:qi5516@qq.com}{qi5516@qq.com}}. We will improve this template together.

\end{Abstract}
% 英文关键词
\begin{KeyWords}
    \LaTeX template; 
    Graduation thesis of Nanchang Institute of Engineering; 
    The template is designed by: \textbf{EatRice-万琪伟}
\end{KeyWords}